The Unicode Cookbook \linebreak for Linguists

### 2018-02-27 book/chapters/introduction.tex
updates structue of this book section to include new chapter arrangement

Before we deal with these proposals we will first discuss the theoretical
background on text encoding, on the Unicode Standard, and on the International
Phonetic Alphabet. In the remainder of this chapter, we give an extended
introduction to the notion of encoding (Section~\ref{encoding}) and the
principles of writing systems, both from a linguistic perspective
(Section~\ref{linguistic-terminology}) and from the perspective of the Unicode
Consortium (Section~\ref{the-unicode-approach}). We consider the Unicode
Standard to be a breakthrough (and ongoing) development that fundamentally
changed the way we look at writing systems, and we aim to provide here a
slightly more in-depth survey of the many techniques that are available in the
standard. A good appreciation for the solutions that the Unicode Standard also
allows for a thorough understanding of possible pitfalls that one might
encounter when using it in general (Chapter~\ref{unicode-pitfalls}). Linguists are more often interested in using the Unicode Standard with the International Phonetic Alphabet (IPA). We first provide a history of the development of the IPA and early attempts to encode it electronically (Chapter~\ref{the-international-phonetic-alphabet}) before we discuss the rather problematic marriage of the International Phonetic Alphabet (IPA) with the Unicode Standard (Chapter~\ref{ipa-meets-unicode}).

In the second part of the book (Chapters~\ref{orthography-profiles} and
\ref{implementation}) we describe our proposals of how to deal with the Unicode
Standard in the daily practice of (comparative) linguistics. First, we discuss the
challenges of characterizing a writing system. To solve these problems, we
propose the notions of orthography profiles, closely related to Unicode locale
descriptions (Chapter~\ref{orthography-profiles}). Finally, we discuss practical
issues with actual examples (Chapter~\ref{implementation}). We provide reference
implementation of our proposals in R and in Python, available as open-source
libraries. An introduction to these implementations of our proposals is
described in Chapter~\ref{implementation}. Finally, we discuss practical issues
with actual examples in Chapter~\ref{use-cases}.

>>>>

Before we deal with these proposals we will first discuss the theoretical
background on text encoding, on the Unicode Standard, and on the International
Phonetic Alphabet. In the remainder of this chapter, we give an extended
introduction to the notion of encoding (Section~\ref{encoding}) and the
principles of writing systems from a linguistic perspective
(Section~\ref{linguistic-terminology}). In Chapter~\ref{the-unicode-approach}, we 
discuss the notions of encoding and writing systems from the perspective of the Unicode
Consortium. We consider the Unicode
Standard to be a breakthrough (and ongoing) development that fundamentally
changed the way we look at writing systems, and we aim to provide here a
slightly more in-depth survey of the many techniques that are available in the
standard. A good appreciation for the solutions that the Unicode Standard also
allows for a thorough understanding of possible pitfalls that one might
encounter when using it in general (Chapter~\ref{unicode-pitfalls}). Linguists are more often interested in using the Unicode Standard with the International Phonetic Alphabet (IPA). We first provide a history of the development of the IPA and early attempts to encode it electronically (Chapter~\ref{the-international-phonetic-alphabet}) before we discuss the rather problematic marriage of the IPA with the Unicode Standard (Chapter~\ref{ipa-meets-unicode}).

In the second part of the book (Chapters~\ref{practical-recommendations}, \ref{orthography-profiles} \&
\ref{implementation}) we describe our proposals of how to deal with the Unicode
Standard in the daily practice of (comparative) linguistics. First, we provide some 
practical recommendations for using the Unicode Standard and IPA for ordinary 
working linguists and for computer programmers (Chapter~\ref{practical-recommendations}). 
Second, we discuss the
challenges of characterizing a writing system; to solve these problems, we
propose the notions of orthography profiles, closely related to Unicode locale
descriptions (Chapter~\ref{orthography-profiles}). Lastly, we provide an introduction to two open source libraries that we have developed, in Python and R, for working with linguistic data and orthography profiles (Chapter~\ref{implementation}).
